% to choose your degree
% please un-comment just one of the following
\documentclass[bsc,frontabs,twoside,singlespacing,parskip,deptreport]{infthesis}     % for BSc, BEng etc.
% \documentclass[minf,frontabs,twoside,singlespacing,parskip,deptreport]{infthesis}  % for MInf

\usepackage{bookmark}

\begin{document}

\title{Build a website to share and discuss software packages}

\author{Qais Patankar}

% to choose your course
% please un-comment just one of the following
% \course{Artificial Intelligence and Computer Science}
%\course{Artificial Intelligence and Software Engineering}
%\course{Artificial Intelligence and Mathematics}
%\course{Artificial Intelligence and Psychology }
%\course{Artificial Intelligence with Psychology }
%\course{Linguistics and Artificial Intelligence}
\course{BEng Computer Science}
%\course{Software Engineering}
%\course{Computer Science and Electronics}
%\course{Electronics and Software Engineering}
%\course{Computer Science and Management Science}
%\course{Computer Science and Mathematics}
%\course{Computer Science and Physics}
%\course{Computer Science and Statistics}

% to choose your report type
% please un-comment just one of the following
%\project{Undergraduate Dissertation} % CS&E, E&SE, AI&L
%\project{Undergraduate Thesis} % AI%Psy
\project{4th Year Project Report}

\date{\today}

\abstract{

!!TODO!! THIS SECTION IS JUST THE PROJECT DESCRIPTION RN !!TODO!!

These software packages are in the form of ``resources''. Resources are archives containing a metadata files, scripts and other miscellaneous files.

Resources can have assets attached in the form of YouTube videos or screenshots. Users can comment on resources, vote on comments, and it should be possible for authors or other users to respond to comments (similar, but not restricted to, a Q\&A format).

Resources can also be dependent on other resources (dependencies). It should be easy to download a resource (or a tree of resources, when we considered dependencies) — this can either be through the web interface or through a companion CLI.

These resources contain code that may be downloaded and executed by other users, so security must be considered. It must be possible for website administrators to easily (bulk) review resources and leave feedback for resource creators. There could also be some inbuilt heuristics to automatically determine whether or not a resource is dangerous.

Users should be able to showcase the projects they have worked on. It should also be possible for multiple users to collaborate on a project together.
}

\maketitle

\section*{Acknowledgements}
Thank you to my supervisor, Stephen Gilmore, for TODO.

!!TODO!!

\tableofcontents

%\pagenumbering{arabic}
